---
title: "Project 2: STAT302package Tutorial"
author: "Jack Go"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{STAT302package Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(STAT302package)
```

# Introduction

This package was created for STAT 302. It includes the following functions:

\code{my_t_test}
\code{my_lm}
\code{my_knn_cv}
\code{my_rf_cv}

In order to install this package from GitHub, you will need to input the following code into your console:

```{r, eval = FALSE}
devtools::install_github("jackgo1889/STAT302package")
library(STAT302package)
```

# A tutorial for my_t_test



First, we must load our example data frame, \code{my_gapminder}, and extract only the \code{lifeExp} data to be used as our \code{x} variable. *Note: Tidyverse is needed.*

```{r}
library(tidyverse)
data("my_gapminder")
example_data <- my_gapminder %>% pull(lifeExp)
```

Now that we have our data, we will perform three tests demonstrating \code{my_t_test}.

We will test our alternative hypothesis being either less than 60, greater than 60, or both, given that the null hypothesis is 60.

```{r}
my_
```


